\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage{multicol}
\usepackage{helvet} % Default font is the helvetica postscript font
\usepackage{verbatim}
\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}
\moveleft.5\hoffset\centerline{\large\bf Hardik Bansal} % Your name at the top
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
\moveleft0.5\hoffset\centerline{Dept. of Computer Science and Technology}
\moveleft0.5\hoffset\centerline{Indian Institute of Technology, Kanpur} % Your address
\moveright1.4\hoffset\centerline{{\bf Email}: hardik@iitk.ac.in} % Your address
\moveright1.2\hoffset\centerline{{\bf Homepage}: home.iitk.ac.in/~hardik} % Your address
\begin{resume}
\section{RESEARCH INTEREST}
Quantum Error Correction and Quantum Cryptography and Graph Theory \\
\section{EDUCATION}
{\sl B.Tech,} Computer Science and Technology \\
Indian Institute of Technology,Kanpur, expected May 2016 \\
\begin{itemize}
\item CGPA(after 2 sems): {\bf 8.7}
\item Precentage (10+2): {\bf 88.7\%}
\item GPA(High School): {\bf 9.6}
\end{itemize}
\section{SHOLASTIC ACHIEVEMENTS}
\begin{itemize}
\item Secured All India Rank {\bf 167} in {\bf IIT-JEE} among 500,000 candidates.
\item Secured All India Rank {\bf 404} in {\bf AIEEE} among 1,000,000 candidates.
\item Selected for the Indian National Astronomy Olympiad({\bf INAO}) amomg {\bf top 30} students in India.
\item Ranked {\bf 5} in Regional Mathematics Olympiad({\bf RMO}).
\item Selected for {\bf ACM-ICPC} 2013 regionals to be held in this December.
\item Selected in {\bf Top 1\%} of INAO(2011,2012), InPHO(2011,2012)
\end{itemize}
\section{COMPUTER \\ SKILLS} 
{\sl {\bf Coding Languages}:} C, C++, Python, Perl, Java, Bash, HTML, Javascript, CSS, XML, MySQL \\
{\sl {\bf Other tools}:} Matlab, GNU Octave, Latex.\\
{\sl {\bf Operating Systems}:} Windows, Linux
\section{PROJECTS}
{\bf Planar Graph Visualisation} \hfill Jan-Apr 2013 \hfill {\sl Mentor: Rizwzn Hudda} \\ 
Studied basic Graph Theory and Algorithms along with various properties of Planar Graphs and heuristics of Graph drawing. Studied various methods to minimize crossings in Planar Graph Drawing for different type of data.\\\\
{\bf Content Based Email Classifier} \hfill May-June 2013 \hfill {\sl Mentor: Ayush Mittal} \\
{\bf Summer Project:} Studied and Implemented various Supervised Machine Learning Algorithms like SVM, Forest Tree, Naive Bayes etc. to classify Emails into five pre-defined categories based on their content. We also analyze the working of various algorithms. \\\\
{\bf Data Compression} \hfill Sept-Nov 2013 \hfill {\sl Mentor: Prof. Sumit Ganguly}\\
{\bf Course Project:} Main Aim of this project was to study the importance of Data Structures in various Data Compression techniques mainly "Lossless Data Compression" like "Huffman Encoding", "Shannon Encoding", "LZ77/LZW" etc. Implemented Huffman and LZ77 encoding.\\
\section{OTHER ACTIVITIES}
\begin{itemize}
\item Involved in discussion sessions based on algorithmic problems with {\bf Prof. Surender Baswana} during last summers.
\item Studied and involved in various online lecture series on Quantum Computing.
\item Read some research papers on {\bf Quantum Error Correction} and {\bf Quantum Cryptography}.
\item Got Appreciation Award for course project in Engineering Graphics course.
\item Won in various Inter and Intra College {\bf Astronomy Competitions}.
\end{itemize}
\section{RELEVANT COURSES}
\begin{multicols}{2}
\begin{itemize}
\item Data Structres and Algorithms
\item Linear Algebra
\item Complex Numbers
\item Partial Differential Equation
\item Computing Lab
\item Real Analysis
\end{itemize}
\end{multicols}
\section{POSITION OF RESPONSIBILITIES}
\begin{itemize}
\item {\bf Student Guide} - Mentored six freshmen in coordination with a team of professional counsellors.
\item {\bf Academic Mentor(Mathematics)} - Providing academic assistance to those students in Mathematics courses(Real Analysis, Linear Algebra).
\item {\bf Coordinator (Computing Events)} - Appointed as Coordinator of Computing Events in Techkriti,2014 (Annual Technical festival of IITK).
\end{itemize}
\end{resume}
\end{document}